Identification of protoneutron star g-modes in gravitational-wave data \pcd{[PCD: alt. title]Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.}

### 2020-09-23 results.tex
add dmax

\hline
\multirow{2}{*}{aLIGO} & $d_{max}$ (kpc) & 7.3  & 26.3 & 24.8 & 22.3 & 16.3 & 10.8 & 7.8  & 14.8\\
\cline{2-10}
                       & SNR            & 13.0 & 37.0 & 38.7 & 39.2 & 22.9 & 23.3 & 75.6 & 63.6\\
\hline
\hline

  \end{tabular}
  \caption{%%
    Matched filter signal-to-noise ratio (SNR) of the simulated waveforms for
    the different GW detectors considered in this study. The source is located
    at 10 kpc and is optimally oriented with respect to the detector.
    %%
  }
  \label{tab:results}
\end{table}

>>>>

\hline
\multirow{2}{*}{aLIGO} & $d_{max}$ & 7  & 26 & 24 & 22 & 16 & 10 & 13 & 28\\
\cline{2-10}
                       & SNR      & 14 & 46 & 33 & 35 & 27 & 21 & 96 & 80\\
\hline
\hline
\multirow{2}{*}{CE1} & $d_{max}$ &  75  & 285 & 279 & 230 & 179 & 111 & 164  & 349\\
\cline{2-10}
                       & SNR    &  149 & 490 & 352 & 366 & 282 & 218 & 1006 & 822\\

\hline
\multirow{2}{*}{CE2} & $d_{max}$ & 147  & -- & -- & -- & -- & 207 & --  & --\\
\cline{2-10}
                       & SNR    & 256 & 843 & 608 & 635 & 487 & 382 & 1751 & 1430\\

\hline
\multirow{2}{*}{ET\_B} & $d_{max}$ & 75  & 278 & 274 & 244 & 159 & 107 & 79   & 62\\
\cline{2-10}
                       & SNR      & 138 & 473 & 356 & 379 & 381 & 260 & 1046 & 865\\

\hline
\multirow{2}{*}{ET\_C} & $d_{max}$ & 71  & 271 & 239 & 222 & 154 & 119 & 104  & 165\\
\cline{2-10}
                       & SNR      & 126 & 432 & 320 & 338 & 252 & 213 & 945 & 783\\

\hline
\multirow{2}{*}{ET\_D} & $d_{max}$ & 79  & 306 & 264 & 252 & 179 & 131 & 134  & 349\\
\cline{2-10}
                       & SNR      & 140 & 477 & 352 & 371 & 277 & 227 & 1034 & 859 \\

  \end{tabular}
  \caption{%%
    Maximal distance $d_{max}$ at which the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ is reconstructed
    with good accuracy for a source optimally oreinted with respect to the GW detectors
    considered in this study.
    Matched filter signal-to-noise ratio (SNR) of the simulated waveforms for
    the different GW detectors. The source is located at 10 kpc and is optimally oriented
    with respect to the detector.
    %%
  }
  \label{tab:results}
\end{table}
